\documentclass[margin,line]{resume}

\begin{document}
\name{\Large Athan Reines}
\begin{resume}

	%% Work Experience %%

	\section{\mysidestyle Experience}

	\textbf{Vurb (acquired by Snapchat)}, San Francisco, California \textbar\ www.vurb.com \vspace{1mm}\\
	\textsl{Data Engineer} \hfill \textbf{June 2015 -- December 2015} \vspace{1mm}\\
	\vspace{-4mm}
	\begin{list2}
		\item Built ETL applications for real-time monitoring of server infrastructure.
		\item Built Node.js microservices for user analytics ingestion and persistence.
		\item Built an ETL pipeline for migrating data from PostgreSQL into InfluxDB and Redshift.
	\end{list2}
	\vspace{-1.5mm}

	\textbf{NodePrime (acquired by Ericsson)}, San Francisco, California \vspace{1mm}\\
	\textsl{Data Scientist/Engineer} \hfill \textbf{September 2013 -- February 2015} \vspace{1mm}\\
	\vspace{-4mm}
	\begin{list2}
		\item Researched and implemented similarity measures for machine inventories to provide insight into datacenter topology.
		\item  Implemented visual methods to infer machine heterogeneity and anomalies.
		\item Built Node.js microservices for machine data analytics and visualization.
	\end{list2}
	\vspace{-1.5mm}

	\textbf{DECODED$^*$}, London, United Kingdom \textbar\ www.decoded.com \vspace{1mm}\\
	\textsl{Data Scientist} \hfill \textbf{August 2012 -- August 2013} \vspace{1mm}\\
	\vspace{-4mm}
	\begin{list2}
		\item Designed and developed the Data Visualization in a Day product.
		\item Led 1-day intensive workshops to help clients leverage data APIs and web-based frameworks to create interactive data visualizations for business intelligence and insight.
	\end{list2}
	\vspace{-1.5mm}

	%% Projects %%

	\section{\mysidestyle Projects}

	\textbf{stdlib} \textbar\ www.stdlib.rocks \vspace{1mm}\\
    \textsl{Project Lead} \hfill \textbf{December 2015 -- present} \vspace{1mm}\\
	\vspace{-4mm}
    \begin{list2}
		\item Lead development of an \textbf{open source} standard library for JavaScript and Node.js, with an emphasis on numerical and scientific computing applications.
		\item Wrote low-level bindings for BLAS and LAPACK.
		\item Implemented standard math library functions and PRNGs.
		\item Implemented a high-performance ndarray API for multi-dimensional data.
		\item Wrote tools for automation (continuous integration, testing, benchmarking, static analysis, and document processing and transformation).
	\end{list2}
	\vspace{-1.5mm}

	%% Education %%

	\section{\mysidestyle Education}

	\textbf{University of Oxford}, Oxford, United Kingdom \vspace{1mm}\\
	\textsl{Doctor of Philosophy} (Condensed Matter Physics) \hfill \textbf{ October 2008 -- December 2012} \vspace{1mm}\\
	\vspace{-4mm}
	\begin{list2}
		\item Thesis: \textit{Analysis methods for single-molecule fluorescence spectroscopy}
		\item Trained hidden Markov models (HMMs) on single-molecule fluorescence time series to uncover hidden state trajectories and reaction kinetics.
		\item Implemented multi-pass algorithms for change-point detection using sliding window t-tests.
		\item Developed visual techniques for analyzing biological time series data.
		\item Wrote Markov chain Monte Carlo simulations to model biological reactions.
	\end{list2}
	\vspace{-1.5mm}

	\textbf{Washington University}, St. Louis, Missouri, United States \vspace{1mm}\\
	\textsl{Post-Baccalaureate Certificate in Premedical Studies} \hfill \textbf{ September 2007 -- May 2008} \vspace{1mm}\\
	\vspace{-4mm}
	\begin{list2}
		\item GPA: 3.70 (4.0 scale)
	\end{list2}
	\vspace{-1.5mm}

	\textbf{Saint Peter's University}, Jersey City, New Jersey, United States \vspace{1mm}\\
	\textsl{Bachelor of Science} \hfill \textbf{ September 2003 -- May 2007} \vspace{1mm}\\
	\vspace{-4mm}
	\begin{list2}
		\item Majors: Physics, Mathematics, Philosophy
		\item Minor: Biology
		\item GPA: 3.98 (4.0 scale)
		\item Valedictorian, Class of 2007; Honors Summa Cum Laude
	\end{list2}
	\vspace{-1.5mm}

	%% Skills %%

	\section{\mysidestyle Skills}

	\begin{list2}
		\item JavaScript, Node.js, WebAssembly
		\item Bash, GNU Make, AWK, Git
		\item Fortran, C
		\item MATLAB/Octave, R, Python, Julia
		\item HTML, CSS, SVG, Markdown
	\end{list2}

\end{resume}
\end{document}
